A convenient, flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate

### 2022-06-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@

% The normalization at z=0 changes the overal rate / normalization
We find that parameter variations that affect shape of \SFRDzZ at low redshift primarily change the normalisation of the mass distribution (see also  $\mathcal{R}_{0.2}$, the total BBH merger rate at redshift 0.2, annotated in the legends of Figure \ref{fig: mass dists}). 
These variations include the width of the cosmic metallicity distribution at $z=0$, $\omega_0$, the mean metallicity of the cosmic metallicity distribution at $z=0$, $\mu_0$, and the skewness of the cosmic metallicity distribution, $\alpha$ (left column of Figure \ref{fig: mass dists}).
Model variations that increase the amount of star formation at low metallicity (i.e. for a low mean metallicity $\mu_0=0.015$ and a wide metallicity distribution $\omega_0 = 1.4$ ) increase the predicted BBH merger rate. This is consistent with other work \todo{copy ref from wind paper.}
Although a skewed distribution allows the metallicity distribution to extend to lower values, it simultaniously pushes the expected value of the metallicity distribution to higher values. Hence, the local rate of BBH mergers is lower for the skewed distribution ($\alpha = -3.5$) with respect to the more symmetric variation ($\alpha = -0.9$). However, the total rate of BBH mergers is only changed by about a factor of 2.

@@

We present a flexible analytic expression for the metallicity-dependent starformation rate.
Large uncertainties remain in the shape and normalisation of the star formation rate density throughout the Universe.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\script{SFR_z.py}
\includegraphics[width=\textwidth]{figures/SFR_redshift.pdf}
\caption{Comparison of different \SFRDz
 \label{fig: SFR(z)}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% The normalization at z=0 changes the overal rate / normalization
We find that parameter variations that affect shape of \SFRDzZ at low redshift primarily change the normalisation of the mass distribution (see also  $\mathcal{R}_{0.2}$, the total BBH merger rate at redshift 0.2, annotated in the legends of Figure \ref{fig: mass dists}). 
These variations include the width of the cosmic metallicity distribution at $z=0$, $\omega_0$, the mean metallicity of the cosmic metallicity distribution at $z=0$, $\mu_0$, and the skewness of the cosmic metallicity distribution, $\alpha$ (left column of Figure \ref{fig: mass dists}).
Model variations that increase the amount of star formation at low metallicity (i.e. for a low mean metallicity $\mu_0=0.015$ and a wide metallicity distribution $\omega_0 = 1.4$ ) increase the predicted BBH merger rate. This is consistent with other work that finds merging BBHs form more efficiently at low metallicities \citep[e.g.][]{BelczynskiVink2010, Stevenson+2017,Mapelli2017,Chruslinska2019_effectCO,Broekgaarden+2021b}.

Although a skewed distribution allows the metallicity distribution to extend to lower values, it simultaniously pushes the expected value of the metallicity distribution to higher values. Hence, the local rate of BBH mergers is lower for the skewed distribution ($\alpha = -3.5$) with respect to the more symmetric variation ($\alpha = -0.9$). However, the total rate of BBH mergers is only changed by about a factor of 2.

@@

We present a flexible analytic expression for the metallicity-dependent starformation rate, \SFRDzZ (equations \ref{eq: z log skew}, \ref{eq: sfr1} and \ref{eq: total sfrd}). A flexible model captures the large uncertainties that remain in the shape and normalisation of the star formation rate density throughout the Universe. 
The novelty of the model presented in this work is that it adopts a skewed-lognormal for the distribution of metallicities at every redshift (\dpdZ). The advantage of an analytical expression is that it allows for controlled experiments of the effect of \SFRDzZ on dependent rates, such as the rate and mass distribution of merging BBHs.

We fit our analytical expression for \SFRDzZ to the starforming-gas in the TNG100 simulation, and provide the best fit parameters in Table \ref{tab: fit params}. We show that our model captures the shape and general behaviour of the cosmological simulations well (see Figure \ref{fig: fit SFRD}).
